---
title: "Fundament"
author: "Josef Brejcha"
date: "2018-04-24"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{Fundament}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
# Basis (Fundament) in the Package of the Methods Used  
  
## Basic: Step in the Chain of Power of Two  
  
$M_1 = A$  
$M_2 = (I + Q)*M_1 = A + Q*A$  
$M_3 = A + Q*A + Q^2*A$  
$M_4 = A + Q*A + Q^2*A + Q^3*A = M_2 + (Q^2 + Q^3)*A$  
$M_4 = M_2 +Q^2*(I + Q)*A = M_2 + Q^2*M_2$  
$M_4 = (I + Q^2)*M_2$  
$M_5 = M_4 + Q^4*A$  
$M_6 = M_5 + Q^5*A$  
$M_7 = M_6 + Q^6*A$  
$M_8 = M_7 + Q^7*A = M_6 + (Q^6 + Q^7)*A$  
$M_8 = M_5 + (Q^5 + Q^6 + Q^7)*A = M_4 + (Q^4 + Q^5 + Q^6 + Q^7)*A$  
$M_8 = M_4 + Q^4*(I + Q + Q^2 + Q^3)*A$  
$M_8 = M_4 + Q^4*M_4 = (I + Q^4)*A$  
$...$  
$M_{2n} = (I + Q^n)*M_n, n = 1, 2, 3, ..$  
  
## More Complex  
$M_3 = A + Q*A + Q^2*A$  
$M_4 = A + Q*A + Q^2*A + Q^3*A$  
$M_5 = A + Q*A + Q^2*A + Q^3*A + Q^4*A$  
$M_6 = A + Q*A + Q^2*A + Q^3*A + Q^4*A + Q^5*A$  
$M_6 = (I + Q^3)*M_3$  
$...$  
$M_{3*2^n} = (I + Q^{3*2^{n-1}})*M_{3*2^{n-1}}$,  
$n = 1, 2, 3, ..$  
  
### and  
  
$M_{k{2^{n}}} = (I + Q^{k2^{n-1}})*M_{k2^{n-1}}$,  
$k = 1, 2, 3, .., n = 1, 2, 3, ..$  
```  
```  
## Examples  
  
### For Basic  
  
```{r message=FALSE}  
require(matrixcalc)
An = 2
matmult <- function(A, B){
	C = matrix(numeric(4), 2, 2)
	for (i in 1:2){
		for (j in 1:2){ C[i, j] = sum(A[i, ]*B[, j])}
	}
	return(C)
}
Q = array(c(0.58, 0.53, 0.42, 0.47), c(2, 2))
q = 0
for (i in 1:8){
  q = q + matrix.power(Q, i)
}
print(paste("i =", i))
print(q)
M = Q
I = diag(1, 2, 2)
n = c(1, 2, 4, 8)
for (i in 2:length(n)){
  M = matmult((I + matrix.power(Q, n[i-1])), M)
}
print(paste("n[i] =", n[i]))
print(M)
```  
  
## For More  
  
```{r}  
Q = array(c(0.58, 0.53, 0.42, 0.47), c(2, 2))
k = 3
q = 0
for (i in 1:48){
  q = q + matrix.power(Q, i)
  if (i == k) Qk = q
}
print(paste("i =", i))
print(q)
  
M = Qk
I = diag(1, 2, 2)
n = integer(5)
for (i in 1:5){
  n[i] = k*2^(i-1)
}
print(n)
for (i in 2:length(n)){
  M = matmult((I + matrix.power(Q, n[i-1])), M)
}
print(paste("n[i] =", n[i]))
print(M)
  
